---
title: "Assignment 3"
author: "Yeung Sui Ping-Raissa 3035871587"
date: "2/2/2022"
output: html_document
---

For assignment 3, you need to produce a map based on the method we learned in class. You can find some useful data from the sources suggested in the lecture notes. There is no standard for assignment 3, please choose the aesthetic style you prefer. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# clear the working environment
rm(list=ls())

# set up working directory
setwd("/Users/visitor/Desktop/Assignment_3_YeungSuiPing")
getwd()
```


# Loading libraries
```{r cars}
library(pacman)
p_load("ggplot2", "tidyverse", "sf", "maptools","tigris","ggthemes","viridis")
```


# Importing dataset
```{r}
# Import the world boundaries
data(wrld_simpl)
st_as_sf(wrld_simpl)-> world
# Import the convid related data
vaccination <- read.csv("https://covid.ourworldindata.org/data/owid-covid-data.csv")
```


# Preparing for the data
```{r}
# Data cleaning 
vaccination %>% 
  group_by(iso_code) %>% 
  arrange(desc(date)) %>%
  slice(1:1) %>% 
  ungroup() %>% 
  select(iso_code,location,date,population_density,population,total_vaccinations) %>%  
  na.omit() %>% 
  mutate(total_vaccination_density=population_density/population*total_vaccinations) -> vaccination

# Join world data and vaccination data set together 
world <- geo_join(world,vaccination,"ISO3","iso_code")

```


# Plot the map
```{r}
ggplot(data = world) +
  geom_sf(aes(fill = total_vaccinations), color="#b37400", size=0.3) +
  scale_fill_viridis(option = "cividis", trans = "sqrt",alpha=0.7)+
   xlab("longitude") + 
  ylab("latitude") +
  theme(panel.background = element_rect(fill="white"),
        panel.grid.minor=element_line(colour='gray'))+
  ggtitle("Vaccination density in the world", subtitle = paste0("(",world$date[3],", ", length(unique(world$NAME)), " countries)"))

ggsave("Vaccination density in the world.png",
       dpi = 1200, width = 6, height = 5)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
